Biologically-Constrained 3D Agglomeration for Connectome Reconstruction

### 2018-03-14 papers/eccv2018/0_introduction.tex
pass on exp and result

The field of connectomics is concerned about reconstructing the wiring diagram of the brain at nanometer resolutions to enable new insights into the workings of the brain~\cite{haehn2017scalable,kasthuri2015saturated}. 
%Recent advancements in image acquisition using multi-beam serial-section electron microscopy (sSEM) allow researchers to produce terabytes of image data per hour~\cite{hildebrand2017whole}. 
%It is infeasible for domain experts to manually reconstruct this vast amount of image data~\cite{haehn2014design}. 
State-of-the-art automatic 3D reconstruction approaches use voxel-based convolutional neural networks (CNNs) and watershed transform to generate initial segmentation, followed by agglomeration steps~\cite{seymour2016rhoananet,lee2015recursive,nunez2014graph,parag2017anisotropic,ronneberger2015u,zlateski2015image}.
%These \textit{bottom-up pixel-based} methods produce excellent results but still fall short of acceptable error rates for large volumes.
For the agglomeration, most methods do not make use of the biological knowledge of the 3D shape of neural structures.
Reported on small-sized volumes, a simple threshold-based mean agglomeration method can achieve superhuman result~\cite{lee2017superhuman}.
However, it is unclear if it is the case for larger volumes.

>>>>

The field of connectomics is concerned about reconstructing the wiring diagram of the brain at nanometer resolutions to enable new insights into the workings of the brain~\cite{haehn2017scalable,kasthuri2015saturated}. 
%Recent advancements in image acquisition using multi-beam serial-section electron microscopy (sSEM) allow researchers to produce terabytes of image data per hour~\cite{hildebrand2017whole}. 
%It is infeasible for domain experts to manually reconstruct this vast amount of image data~\cite{haehn2014design}. 
State-of-the-art automatic 3D reconstruction approaches use pixel-based convolutional neural networks (CNNs) and watershed transform to generate initial segmentation, followed by agglomeration steps~\cite{seymour2016rhoananet,lee2015recursive,nunez2014graph,parag2017anisotropic,ronneberger2015u,zlateski2015image}.
%These \textit{bottom-up pixel-based} methods produce excellent results but still fall short of acceptable error rates for large volumes.
For the agglomeration, most methods do not make use of the biological knowledge of the 3D shape of neural structures.
Reported on small-sized volumes, a simple threshold-based mean agglomeration method can achieve superhuman result~\cite{lee2017superhuman}.
However, it is unclear if it is the case for larger volumes.

### 2018-03-14 papers/eccv2018/1_related_work.tex
pass on exp and result

\subsubsection{Initial Segmentation}
A significant amount of connectomics research considers the problem of extracting segmentation information at the voxel level from raw EM images.

@@

\subsubsection{Agglomeration}
\TODO{rule-based method}
Some methods rely solely on the accuracy of the predicted affinities and agglomerate hierarchically based on the mean affinity between supervoxels~\cite{lee2017superhuman,funke2017deep}.

\TODO{classification-based method}
Given the initial segmentation, some methods train random-forest classifiers to produce the final segmentations~\cite{seymour2016rhoananet,nunez2014graph,parag2017anisotropic,zlateski2015image,10.1371/journal.pone.0125825}
extract different features
~\cite{jain2011learning,bogovic2013learned}.

\TODO{optimization-based method}
Pape et al. present a scalable multicut algorithm to partition superpixels~\cite{beier2017multicut}.

>>>>

\subsubsection{Pixel-Based Segmentation}
A significant amount of connectomics research considers the problem of extracting segmentation information at the voxel level from raw EM images.

@@

\subsubsection{Agglomeration}
\TODO{rule-based}
Some methods rely solely on the accuracy of the predicted affinities and agglomerate hierarchically based on the mean affinity between supervoxels~\cite{lee2017superhuman,funke2017deep}.

\TODO{classification-based}
Given the initial segmentation, some methods train random-forest classifiers to produce the final segmentations~\cite{seymour2016rhoananet,nunez2014graph,parag2017anisotropic,zlateski2015image,10.1371/journal.pone.0125825}
extract different features
~\cite{jain2011learning,bogovic2013learned}.

\TODO{optimization-based}
Pape et al. present a scalable multicut algorithm to partition superpixels~\cite{beier2017multicut}.

### 2018-03-14 papers/eccv2018/2_method.tex
pass on exp and result

\begin{figure}[t!]
	\centering
	\includegraphics[width=\linewidth]{./figures/teaser_v2.png}
	\caption{Our proposed framework uses both local and global biological constraints to improve an input segmentation.}
	\label{fig:teaser}
\end{figure}
% \begin{figure*}[t!]
% 	\begin{center}
% 		\subfloat[]{\includegraphics[width=0.24\linewidth]{./figures/methods/multicut_input.png}}
% 		\subfloat[]{\includegraphics[width=0.24\linewidth]{./figures/methods/pre-multicut.png}}
% 		\subfloat[]{\includegraphics[width=0.24\linewidth]{./figures/methods/multicut-graph.png}}
% 		\subfloat[]{\includegraphics[width=0.24\linewidth]{./figures/methods/post-multicut.png}}
% 	\end{center}
% 	\caption{Outline of our approach, from left to right: result of the pixel-based segmentation and agglomeration algorithm; segments of several neurons from the initial segmentation; extracted skeletonized network of those segments; improved 3D reconstruction of the selected segments after graph construction and partitioning with constraints.}
% 	\label{fig:overview}
% \end{figure*}

%There are two types of errors that can occur in connectomics segmentations: \textit{split errors} and \textit{merge errors}. 
%In a split error, two segments should have been merged into one neuronal process. 
%In a merge error, one segment corresponds to more than one neuron.
%Generally, it is much more difficult to correct merge errors than to correct split errors, as the space of possible split proposals grows quickly~\cite{parag2015properties}.
%Thus, most reconstruction approaches are tuned towards over-segmentation with many more split than merge errors. 
Our method takes as input over-segmentations of EM image volumes generated by scalable, state-of-the-art connectomics reconstruction pipelines (Sec.~\ref{sec:neuroproof}). 
Our goal is to identify locations of split errors and merge the corresponding segments automatically.

From the input segmentation we generate a graph $G$ with nodes $N$ and edges $E$ with weights $w_e$. 
The nodes correspond to labeled segments from the input data with edges between merge candidates.
We propose the following three steps to formulate and then partition the graph while obeying constraints from the underlying biology.
First, we only consider merging segments based on a skeletonized representation of the input segmentation.
This is enables us to reduce the number of nodes in the graph based on prior knowledge of the shape of neuronal processes.
Second, we train a convolutional neural network that learns biological constraints based on the shapes of the input segmentation.
This network generates probabilities that segments belong to the same neuron based only on the segmentations. 
An example of one such learned constraint is that neurons have small turning radii (Fig.~\ref{fig:turn-radii}).
Third, we partition the graph using a lifted multicut formulation with additional acyclic constraints to enforce global biological constraints.
The lifted multicut solution is globally consistent which we then augment to produce a tree-structured graph (i.e., one with no cycles).

\subsection{Graph Creation}
%\subsubsection{Node Generation}
\label{sec:skeletonization}

\subsubsection{Node Generation}

The simplest node generation strategy creates one node for every unique segment label in the input volume. 
However, some of the labels in the volume correspond to very small structures that are likely the result of segmentation errors, typically in regions with noisy raw image data. 
It is difficult to extract useful shape features from these segments because of their small, often random, shape. 
We prune these nodes from the graph by removing all segments with fewer than a threshold $t_{seg} = 20,000$ voxels. 
This removes on average \TODO{XX}\% of the segments in our  datasets (Sec.~\ref{sec:dataset}), leaving us with around $\TODO{XX}$ nodes per dataset (\TODO{X nodes per micrometer}). 
Despite the large number of segments, these regions only take up \TODO{XX}\% of the total volume on average.

\subsubsection{Edge Generation}

@@

A typical approach for generating edges produces one between all adjacent segments. 
Two segments $l_1$ and $l_2$ are considered adjacent if there is a pair of adjacent voxels with one labeled $l_1$ and the other labeled $l_2$.
For example, pixel-based agglomeration methods such as mean agglomeration~\cite{lee2017superhuman} or waterz~\cite{funke2017deep} consider all pairs of adjacent segments for merging.
However, this method produces too many edges in the graph for graph-based optimization approaches. 
We identify a smaller number of pairs of segments to consider as graph edges using the following approach.

First, we extract a skeleton from each segment in the label volume using a variant~\cite{zhao2014automatic} of the TEASER algorithm~\cite{sato2000teasar}. 
This skeletonization algorithm repeatedly uses Dijkstra's algorithm to find the farthest voxel from a seed location. 
Since this algorithm is non-linear in the number of voxels, we downsample the datasets so that there are voxel samples every $\SI{30}{\nano\meter}$ in each dimension.
Empirically, this reduced the running time for skeletonization by $\TODO{XX\%}$, with minimal reduction in skeleton accuracy ($\TODO{XX\%}$ fewer branches). 
Fig.~\ref{fig:skeletonization} shows four examples of extracted skeletons (in black). 
These skeletons consist of a sequence of \textit{joints}, i.e., locations that are locally a maximum distance from the segment boundary, with line segments connecting successive joints. 
We refer to joints that have only one connected neighbor as \textit{endpoints}. 
We find that approximately \TODO{XX\%} of the segments that are erroneously split have nearby endpoints (Fig.~\ref{fig:merge_candidates}).

Two segments, $s_1$ and $s_2$, receive a corresponding edge if the two following conditions hold.
First, a endpoint in either $s_1$ or $s_2$ is with $t_{low}$ nm of any voxel in the other segment.
Second, there is an endpoint in $s_1$ and an endpoint in $s_2$ that are within $t_{high}$ nm of each other.
We store the midpoints between the two endpoints as the center of the potential merge in the set $\mathbb{S}_c$. 
This algorithm produces a set of segments to consider for merging. 
Only these pairs have a corresponding edge in the constructed graph.

\begin{figure}[t]
	\begin{minipage}{0.45\linewidth}
		\includegraphics[width=\linewidth]{./figures/constraint_error.png}
	\end{minipage}
	\hfill
	\begin{minipage}{0.45\linewidth}
		\includegraphics[width=\linewidth]{./figures/constraint_success.png}
	\end{minipage}
	\caption{Two example candidates for merging. The two segments in the left example do not belong to the same neuron as evidenced by the sharp turning radius.}
	\label{fig:turn-radii}
\end{figure}
\subsection{Edge Weights Assignment}
\label{sec:edge-weights}
We assign edge weights $w_e$ to each edge where the weight corresponds to the probability that two nodes belong to the same neuron.
We train a 3D CNN classifier to learn from the manually labeled oversegmentation input volume (Sec.~\ref{sec:dataset}).
If the probability that the nodes belong to the same neuron is $p_e$, the edge weight $w_e = \log{\frac{p_e}{1 - p_e}} + \log{\frac{1 - \beta}{\beta}}$, where $\beta$ is a tunable parameter that encourages over- or under-segmentation.

\subsubsection{Classifier Input}

We extract a cubic region of interest (ROI) around each endpoint $e$ in $\mathbb{S}_c$ as input to the CNN. 
The CNN receives three input channels for every voxel in the ROI around segments $l_1$ and $l_2$. 
The input in all of the channels is in the range $\{-0.5, 0.5\}$. 
The first channel is $0.5$ only if the corresponding voxel has label $l_1$. 
The second channel is $0.5$ only if the corresponding voxel has label $l_2$. 
The third channel is $0.5$ if the corresponding voxel is either $l_1$ or $l_2$.
We do not use the raw EM image information to avoid the need to retrain the network on datasets that have been stained differently or imaged at different resolution. 
This reduces the need for generating costly manually-labeled ground truth.

\subsubsection{Network Architecture \& Training}

We use \textit{VGG-style} blocks as presented by Chatfield et al.~\cite{chatfield2014return}. 
Each blocks consists of two double convolutions with filter size $3\times3\times3$ followed by a max pooling step. 
There are three layers of these blocks. 
The first two max pooling layers are anisotropic with pooling only in the $x$ and $y$ dimensions. 
The output of this final pooling step is flattened into a 1D vector that is input into two fully connected layers. 
The final layer produces probabilities with a sigmoid activation function~\cite{funahashi1989approximate}. 
All of the other activation functions are LeakyReLU~\cite{maas2013rectifier}.

For training we use a stochastic gradient descent optimizer with Nesterov's accelerated gradient~\cite{nesterov1983method}. 
We employ dropouts of $0.2$ after every pooling layer and the first dense layer, and a dropout of $0.5$ after the final dense layer to prevent overfitting. 
We discuss all other network parameters in Sec.~\ref{sec:network-parameters}.

\subsection{Graph Clustering}

\begin{figure}[t]
	\centering
	\begin{minipage}{0.32\linewidth}
		\includegraphics[width=\linewidth]{./figures/split_error1.png}		
	\end{minipage}
	\hfill
	\begin{minipage}{0.32\linewidth}
		\includegraphics[width=\linewidth]{./figures/split_error2.png}				
	\end{minipage}
	\hfill
	\begin{minipage}{0.32\linewidth}
		\includegraphics[width=\linewidth]{./figures/split_error3.png}
	\end{minipage}
	\caption{Three erroneously split segments.}
	\label{fig:merge_candidates}
\end{figure}
\subsubsection{Lifted Multicut}

After constructing the 3D graph we seek to partition the graph into labels where every label corresponds to a neuronal process. 
We formulate this graph partitioning problem as a multicut problem.
There are two primary benefits to using a multicut formulation. 
First, the number of segments in the final graph is not predetermined but depends on the input graph itself. 
Second, this minimization produces globally consistent solutions (i.e. a boundary remains if and only if the two corresponding nodes belong to unique segments)~\cite{keuper2015efficient}.

@@

\subsubsection{Topological Constraints}

By reformulating the segmentation problem as a graph partitioning one, we can enforce some global constraints on our result based on the underlying biology.
Traditional hierarchical clustering algorithms do not rely on such constraints but consider local decisions independently.
We enforce a global constraint that neurons are tree-structured and should not contain cycles. 
The multicut problems returns a series of ``collapsed'' edges between nodes that belong to the same neuron.
We iterate over these edges in order of the probability of merge generated by our CNN. 
We ``collapse'' an edge only if it does not create a cycle in the graph.

>>>>

\begin{figure}[t!]
	\centering
	\includegraphics[width=\linewidth]{./figures/teaser_v2.png}
	\caption{Our proposed framework uses both local and global biological constraints to improve an input segmentation.}
	\label{fig:teaser_pipeline}
\end{figure}
% \begin{figure*}[t!]
% 	\begin{center}
% 		\subfloat[]{\includegraphics[width=0.24\linewidth]{./figures/methods/multicut_input.png}}
% 		\subfloat[]{\includegraphics[width=0.24\linewidth]{./figures/methods/pre-multicut.png}}
% 		\subfloat[]{\includegraphics[width=0.24\linewidth]{./figures/methods/multicut-graph.png}}
% 		\subfloat[]{\includegraphics[width=0.24\linewidth]{./figures/methods/post-multicut.png}}
% 	\end{center}
% 	\caption{Outline of our approach, from left to right: result of the pixel-based segmentation and agglomeration algorithm; segments of several neurons from the initial segmentation; extracted skeletonized network of those segments; improved 3D reconstruction of the selected segments after graph construction and partitioning with constraints.}
% 	\label{fig:overview}
% \end{figure*}

%There are two types of errors that can occur in connectomics segmentations: \textit{split errors} and \textit{merge errors}. 
%In a split error, two segments should have been merged into one neuronal process. 
%In a merge error, one segment corresponds to more than one neuron.
%Generally, it is much more difficult to correct merge errors than to correct split errors, as the space of possible split proposals grows quickly~\cite{parag2015properties}.
%Thus, most reconstruction approaches are tuned towards over-segmentation with many more split than merge errors. 
The input of our method is the over-segmentation of EM image volumes from state-of-the-art pipelines.
Our pipeline is illustrated in Fig.~\ref{fig:teaser_pipeline}.
%Our goal is to identify locations of split errors and merge the corresponding segments automatically.

\TODO{[refer to teaser figure of the pipeline]}
\TODO{[need to be concise here]}
\TODO{[we use biological constraints]}
From the input segmentation we generate a graph $G$ with nodes $N$ and edges $E$ with weights $w_e$. 
The nodes correspond to labeled segments from the input data with edges between merge candidates.
We propose the following three steps to formulate and then partition the graph while obeying constraints from the underlying biology.
First, we only consider merging segments based on a skeletonized representation of the input segmentation.
This is enables us to reduce the number of nodes in the graph based on prior knowledge of the shape of neuronal processes.
Second, we train a convolutional neural network that learns biological constraints based on the shapes of the input segmentation.
This network generates probabilities that segments belong to the same neuron based only on the segmentations. 
An example of one such learned constraint is that neurons have small turning radii (Fig.~\ref{fig:turn-radii}).
Third, we partition the graph using a lifted multicut formulation with additional acyclic constraints to enforce global biological constraints.
The lifted multicut solution is globally consistent which we then augment to produce a tree-structured graph (i.e., one with no cycles).

\subsection{Skeleton-Based Graph Generation}
%\subsubsection{Node Generation}
\label{sec:skeletonization}
Most agglomeration methods create the region graph by removing small-sized segments and linking each pair of adjacent segments, which can still lead to a large graph size due to the irregular shape of neural structures.
We here use the skeleton representation of the segmenation and reduce the graph size with the geometric constraints on the connectivity of two adjacent segments to prune edges.
% a bit trivial, as everyone is doing this. maybe no need to mention
% \subsubsection{Node Pruning}
% %The simplest node generation strategy creates one node for every unique segment label in the input volume. 
% Some labels in the volume correspond to very small structures that are likely the result of segmentation errors, typically in regions with noisy raw image data. 
% It is difficult to extract useful shape features from these segments because of their small, often random, shape. 
% We prune these nodes from the graph by removing all segments with fewer than a empirical threshold $t_{seg} = 20,000$ voxels. 
% This removes on average \TODO{XX}\% of the segments in our  datasets (Sec.~\ref{sec:dataset}), leaving us with around $\TODO{XX}$ nodes per dataset (\TODO{X nodes per micrometer}). 
% Despite the large number of segments, these regions only take up \TODO{XX}\% of the total volume on average.

% \subsubsection{Edge Pruning}

@@

%A typical approach for generating edges produces one between all adjacent segments. 
%Two segments $l_1$ and $l_2$ are considered adjacent if there is a pair of adjacent voxels with one labeled $l_1$ and the other labeled $l_2$.
%For example, pixel-based agglomeration methods such as mean agglomeration~\cite{lee2017superhuman} or waterz~\cite{funke2017deep} consider all pairs of adjacent segments for merging.
%However, this method produces too many edges in the graph for graph-based optimization approaches. 
Our key observation is that if two segments belong to the same neural structure, their skeleton end points should satisfy certain geomtry constraints.
%We identify a smaller number of pairs of segments to consider as graph edges using the following approach.

To extract the skeleton from each segment, we use a variant~\cite{zhao2014automatic} of the TEASER algorithm~\cite{sato2000teasar}. 
This skeletonization algorithm repeatedly uses Dijkstra's algorithm to find the farthest voxel from a seed location. 
Since this algorithm is non-linear in the number of voxels, we downsample the datasets so that there are voxel samples every $\SI{30}{\nano\meter}$ in each dimension.
Empirically, this reduced the running time for skeletonization by $\TODO{XX\%}$, with minimal reduction in skeleton accuracy ($\TODO{XX\%}$ fewer branches). 
Fig.~\ref{fig:skeletonization} shows four examples of extracted skeletons (in black). 
These skeletons consist of a sequence of \textit{joints}, i.e., locations that are locally a maximum distance from the segment boundary, with line segments connecting successive joints. 
We refer to joints that have only one connected neighbor as \textit{endpoints}. 
We find that approximately \TODO{XX\%} of the segments that are erroneously split have nearby endpoints (Fig.~\ref{fig:merge_candidates}).

\TODO{maybe good to have equation, to make the biological constraints stand out more}
Two segments, $s_1$ and $s_2$, receive a corresponding edge if the two following conditions hold. \TODO{what's the intuition}
First, a endpoint in either $s_1$ or $s_2$ is with $t_{low}$ nm of any voxel in the other segment.
Second, there is an endpoint in $s_1$ and an endpoint in $s_2$ that are within $t_{high}$ nm of each other.
We store the midpoints between the two endpoints as the center of the potential merge in the set $\mathbb{S}_c$. 
This algorithm produces a set of segments to consider for merging. 
Only these pairs have a corresponding edge in the constructed graph.

\begin{figure}[t]
	\begin{minipage}{0.45\linewidth}
		\includegraphics[width=\linewidth]{./figures/constraint_error.png}
	\end{minipage}
	\hfill
	\begin{minipage}{0.45\linewidth}
		\includegraphics[width=\linewidth]{./figures/constraint_success.png}
	\end{minipage}
	\caption{Two example candidates for merging. The two segments in the left example do not belong to the same neuron as evidenced by the sharp turning radius.}
	\label{fig:turn-radii}
\end{figure}
\subsection{Learning-based Edge Weight}
\label{sec:edge-weights}
We aim to assign edge weights $w_e$ to each edge corresponding to the possibility of two nodes belonging to the same neural structure.
W, we train a 3D CNN model to learn these geometric contraints for valid connection between two segments from labeled volume.

\noindent\textbf{Edge Probability}
As it's hard to manually design the weight
Below, we describe the network we trained to predict $p_e$.

%\subsubsection{Network Architecture}
Our network is a feedforward convolutional network with three \textit{VGG-style} convolution blocks~\cite{chatfield2014return} and two fully connected layers before the final sigmoid activation. 
Each \textit{VGG-style} convolution block consists of two double convolutions with filter size $3\times3\times3$ and LeakyReLU(0.0005), followed by a max pooling with filter size \TODO{xx}.

For the input of the network, we extract a cubic region of interest (ROI) around each endpoint $e$ in $\mathbb{S}_c$ as input to the CNN. 
The CNN receives three input channels for every voxel in the ROI around segments $l_1$ and $l_2$. 
The input in all of the channels is in the range $\{-0.5, 0.5\}$. 
The first channel is $0.5$ only if the corresponding voxel has label $l_1$. 
The second channel is $0.5$ only if the corresponding voxel has label $l_2$. 
The third channel is $0.5$ if the corresponding voxel is either $l_1$ or $l_2$.
We do not use the raw EM image information to avoid the need to retrain the network on datasets that have been stained differently or imaged at different resolution. 
This reduces the need for generating costly manually-labeled ground truth.

\noindent\textbf{Edge Weight}
To add more control.. \TODO{what's the intuition}
Given the probability that the nodes belong to the same neuron is $p_e$, the edge weight $w_e$ is defined as
%p_e &=\mbox{CNN}(x_1, x_2) \\
\begin{align}
w_e = \log{\frac{p_e}{1 - p_e}} + \log{\frac{1 - \beta}{\beta}}
\end{align}
, where $\beta$ is a tunable parameter that encourages over- or under-segmentation. 
%The first two max pooling layers are anisotropic with pooling only in the $x$ and $y$ dimensions. 
%The output of this final pooling step is flattened into a 1D vector that is input into . 
%The final layer produces probabilities with a sigmoid activation function~\cite{funahashi1989approximate}. 
%All of the other activation functions are .

% covered in the experiment
%For training we use a stochastic gradient descent optimizer with Nesterov's accelerated gradient~\cite{nesterov1983method}. 
%We employ dropouts of $0.2$ after every pooling layer and the first dense layer, and a dropout of $0.5$ after the final dense layer to prevent overfitting. 
%We discuss all other network parameters in Sec.~\ref{sec:network-parameters}.

\begin{figure}[t]
	\centering
	\begin{minipage}{0.32\linewidth}
		\includegraphics[width=\linewidth]{./figures/split_error1.png}		
	\end{minipage}
	\hfill
	\begin{minipage}{0.32\linewidth}
		\includegraphics[width=\linewidth]{./figures/split_error2.png}				
	\end{minipage}
	\hfill
	\begin{minipage}{0.32\linewidth}
		\includegraphics[width=\linewidth]{./figures/split_error3.png}
	\end{minipage}
	\caption{Three erroneously split segments.}
	\label{fig:merge_candidates}
\end{figure}
\subsection{Optimization-Based Graph Partition}
intro: blah,blah. \TODO{can we have a formula here?}

%\subsubsection{Lifted Multicut}
\noindent\textbf{Lifted Multicut}
After constructing the 3D graph we seek to partition the graph into labels where every label corresponds to a neuronal process. 
We formulate this graph partitioning problem as a multicut problem.
There are two primary benefits to using a multicut formulation. 
First, the number of segments in the final graph is not predetermined but depends on the input graph itself. 
Second, this minimization produces globally consistent solutions (i.e. a boundary remains if and only if the two corresponding nodes belong to unique segments)~\cite{keuper2015efficient}.

@@

%\subsubsection{Topological Constraints}
\noindent\textbf{Topological Constraints}
By reformulating the segmentation problem as a graph partitioning one, we can enforce some global constraints on our result based on the underlying biology.
Traditional hierarchical clustering algorithms do not rely on such constraints but consider local decisions independently.
We enforce a global constraint that neurons are tree-structured and should not contain cycles. 
The multicut problems returns a series of ``collapsed'' edges between nodes that belong to the same neuron.
We iterate over these edges in order of the probability of merge generated by our CNN. 
We ``collapse'' an edge only if it does not create a cycle in the graph.
